The development of infants' responses to mispronunciations: A Meta-Analysis

### 2020-11-10 VonHolzenBergmann_MPMetaAnalysis.tex
acceptance!

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man, noextraspace]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={The development of infants' responses to mispronunciations: A Meta-Analysis},
  pdfauthor={Katie Von Holzen1,2,3 \& Christina Bergmann4,5},
  pdflang={en-EN},
  pdfkeywords={language acquisition; mispronunciation sensitivity; word recognition; meta-analysis; lexicon; infancy},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\title{The development of infants' responses to mispronunciations: A Meta-Analysis}
\author{Katie Von Holzen\textsuperscript{1,2,3} \& Christina Bergmann\textsuperscript{4,5}}
\date{}

@@

The authors each declare that they have no conflict of interest.

@@

\affiliation{\vspace{0.5cm}\textsuperscript{1} Lehrstuhl Linguistik des Deutschen, Schwerpunkt Deutsch als Fremdsprache/Deutsch als Zweitsprache, Technische Universität Dortmund\\\textsuperscript{2} Department of Hearing and Speech Sciences, University of Maryland, USA\\\textsuperscript{3} Laboratoire Psychologie de la Perception, Université Paris Descartes\\\textsuperscript{4} Max Planck Institute for Psycholinguistics, Nijmegen, the Netherlands\\\textsuperscript{5} LSCP, Departement d'Etudes Cognitives, ENS, EHESS, CNRS, PSL Research University}

@@

The first set of questions concerns how infants' sensitivity is modulated by different kinds of mispronunciations. Following on the above example, some experiments examine infants' sensitivity to factors that change the identity of a word on a measurable level, or \emph{mispronunciation size} (i.e.~1-feature, 2-features, 3-features), finding that infants are more sensitive to larger mispronunciations (3-feature-changes) than smaller mispronunciations (1-feature changes) for both consonant (Bernier \& White, 2017; Tamasi, 2016; White \& Morgan, 2008) and vowel (Mani \& Plunkett, 2011) mispronunciations, known as graded sensitivity. By aggregating studies testing infants of different ages on mispronunciations of varying size, this also has consequences for understanding whether graded sensitivity changes over development.

@@

We next considered whether an effect of maturation might have been masked by other factors we have not yet captured in our analyses. A strong candidate that emerged during the construction of the present dataset and careful reading of the original papers was the analysis approach. We observed, as mentioned in the Methods section, variation in the dependent variable reported, and additionally noted that the size of the chosen post-naming analysis window varied substantially across papers. Researchers' analysis strategy may be adapted to infants' age or influenced by having observed the data. For example, consider the possibility that a particular study does not find that infants looked to the target object upon hearing a correct pronunciation. With this pattern of behavior, interpreting an effect of mispronunciation sensitivity becomes difficult; how can infants notice a phoneme change when they do not even show recognition of the correct pronunciation? A lack of recognition or a small effect for correct pronunciations would be more difficult to publish (Ferguson \& Heene, 2012). In order to have publishable results, adjustments to the analysis approach could be made until a significant effect of recognition for correct pronunciations is found. But, these adjustments would also need to be made for the analysis of mispronunciations, which may impact the size of the mispronunciation sensitivity effect. Such a scenario could explain the publication bias suggested by the asymmetry for correct pronunciations in the funnel plot shown in Figure \ref{fig:FunnelCombo} (Simmons, Nelson, \& Simonsohn, 2011). This could lead to an increase in significant results and even alter the apparent developmental trajectory of mispronunciation sensitivity measured in experiments.

@@

Considering the variation in findings of developmental change in mispronunciation sensitivity (see Introduction), we next evaluated the developmental trajectory of infants' mispronunciation sensitivity. Our analysis of this relationship revealed a pattern of unchanging sensitivity over infant age and vocabulary size, which has been reported by a handful of studies directly comparing infants over a small range of ages, such as 18-24 months (Bailey \& Plunkett, 2002; Swingley \& Aslin, 2000) or 12-17 months (Zesiger et al., 2012). The lack of age or vocabulary effects in our meta-analysis suggest that this understanding is present from an early age and is maintained throughout early lexical development. We note, however, that despite an increasing publication record of mispronunciation sensitivity studies, fewer than half of the papers included in this meta-analysis measured vocabulary (\emph{n} = 13; out of 32 papers total; see also Figure \ref{fig:Vocabdescribe1}). On the one hand, this may reflect a decreasing interest in the relationship between mispronunciation sensitivity and vocabulary size and/or to invest in data collection that is not expected to yield significant outcomes. On the other hand, non-significant correlations between mispronunciation sensitivity and vocabulary size may be more likely to not be reported, reducing our ability to uncover the true relationship (Rosenthal, 1979; Simonsohn et al., 2014). Considering the theoretical implications, however, more experimental work investigating and reporting the relationship between mispronunciation sensitivity and vocabulary size, whether the relationship is significant or not, is needed if this link is to be evaluated. We encourage researchers to measure and report infants' vocabulary size in future studies. Nonetheless, if we are to take our results as robust, it becomes thus a pressing open question that theories have to answer which other factors might prompt acquiring and using language-specific phonological contrasts at such an early age.

@@

For several moderators, we found no evidence of significant modulation of mispronunciation sensitivity. Studies that include an unfamiliar, as opposed to familiar distractor image, often argue that the unfamiliar image provides a better referent candidate for mispronunciation than a familiar distractor image, where the name is already known. Yet, no studies have directly examined this assertion and our meta-analysis found that distractor familiarity did not significantly modulate mispronunciation sensitivity. One possible explanation is that when the size of the mispronunciation is small (e.g.~1-feature change), infants are unlikely to map this label onto a novel object (for evidence from infant word learning see Dautriche, Swingley, \& Christophe, 2015; Swingley, 2016; Swingley \& Aslin, 2007).

@@

Variation in measurement standards can have serious consequences, as our analyses show, limiting our ability to draw conclusions. We take this opportunity to make several recommendations to address the issue of varying, potentially post hoc analysis decisions. First, preregistration can serve as proof of a priori decisions regarding data analysis, which can also contain a data-dependent description of how data analysis decisions will be made once data is collected (see Havron, Bergmann, \& Tsuji, 2020 for a primer). The peer-reviewed form of preregistration, Registered Reports, has already been adopted by a large number of developmental journals, and general journals that publish developmental works, showing the field's increasing acceptance of such practices for hypothesis-testing studies. Second, sharing data (Open Data) can allow others to re-analyze existing datasets to both examine the impact of analysis decisions and cumulatively analyze different datasets in the same way. Considering the specific issue of analysis time window, experimenters can opt to analyze the time course as a whole, instead of aggregating the proportion of target looking behavior. This allows for a more detailed assessment of infants' fixations over time and removes the need to reduce the post-naming analysis window. Both Growth Curve Analysis (Mirman, Dixon, \& Magnuson, 2008) and Permutation Clusters Analysis (Maris \& Oostenveld, 2007; Von Holzen \& Mani, 2012) offer potential solutions to analyze the full time course (although Growth Curve Analyses are not without criticism, see Huang \& Snedeker, 2020). Third, it may be useful to establish standard analysis pipelines for mispronunciation studies. This would allow for a more uniform analysis of this phenomenon, as well as aid experimenters in future research planning (see ManyBabiesConsortium, 2020 for a parallel effort). As mentioned previously, one example of standardization would be for all experimenters to measure and report vocabulary size. We hope the above suggestions take us one step closer to this important goal that clarifies the link between internal abilities and behavior in a laboratory study.

@@

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man, noextraspace]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={The development of infants' responses to mispronunciations: A Meta-Analysis},
  pdfauthor={Katie Von Holzen1,2,3 \& Christina Bergmann4,5, 6},
  pdflang={en-EN},
  pdfkeywords={language acquisition; mispronunciation sensitivity; word recognition; meta-analysis; lexicon; infancy},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\title{The development of infants' responses to mispronunciations: A Meta-Analysis}
\author{Katie Von Holzen\textsuperscript{1,2,3} \& Christina Bergmann\textsuperscript{4,5, 6}}
\date{}

@@

The authors would like to thank Emelyne Gaudichau for valuable assistance in entering data. The data, analysis scripts, and RMarkdown file used in this study to create this manuscript are available on the Open Science Framework (\url{https://osf.io/rvbjs/}). Katie Von Holzen was supported by the Agence Nationale de la Recherche (ANR-13-BSH2-0004) and by training grant DC-00046 from the National Institute of Deafness and Communicative Disorders of the National Institutes of Health. Christina Bergmann was supported by H2020 European Research Council Marie Skłodowska-Curie grant No 660911; the Département d'Etudes Cognitives (DEC) ANR-17-EURE-0017, the Berkeley Initiative for Transparency in the Social Sciences, a program of the Center for Effective Global Action (CEGA), with support from the Laura and John Arnold Foundation. The authors each declare that they have no conflict of interest.

@@

\affiliation{\vspace{0.5cm}\textsuperscript{1} Lehrstuhl Linguistik des Deutschen, Schwerpunkt Deutsch als Fremdsprache/Deutsch als Zweitsprache, Technische Universität Dortmund, Germany\\\textsuperscript{2} Department of Hearing and Speech Sciences, University of Maryland, USA\\\textsuperscript{3} Université Paris Descartes, Sorbonne Paris Cité, Paris, France\\\textsuperscript{4} CNRS (Integrative Neuroscience and Cognition Center, UMR 8002), Paris, France\\\textsuperscript{5} Max Planck Institute for Psycholinguistics, Nijmegen, the Netherlands\\\textsuperscript{6} Laboratoire de Sciences Cognitives et de Psycholinguistique, Département d'études cognitives, ENS, EHESS, CNRS, PSL University}

@@

The first set of questions concerns how infants' sensitivity is modulated by different kinds of mispronunciations. Following on the above example, some experiments examine infants' sensitivity to factors that change the identity of a word on a measurable level, or \emph{mispronunciation size} (i.e.~1-feature, 2-features, 3-features), finding that infants are more sensitive to larger mispronunciations (3-feature-changes) than smaller mispronunciations (1-feature changes) for both consonant (Bernier \& White, 2017; Tamasi, 2016; White \& Morgan, 2008) and vowel (Mani \& Plunkett, 2011) mispronunciations, known as graded sensitivity. By aggregating studies testing infants of different ages on mispronunciations of varying size, this also has consequences for identifying any graded sensitivity changes over development.

@@

We next considered whether an effect of maturation might have been masked by other factors we have not yet captured in our analyses. A strong candidate that emerged during the construction of the present dataset and careful reading of the original papers was the analysis approach. We observed, as mentioned in the Methods section, variation in the dependent variable reported, and additionally noted that the size of the chosen post-naming analysis window varied substantially across papers. Researchers' analysis strategy may be adapted to infants' age or influenced by having observed the data. For example, consider the possibility that a particular study does not find that infants looked to the target object upon hearing a correct pronunciation. With this pattern of behavior, interpreting an effect of mispronunciation sensitivity becomes difficult; how can infants notice a phoneme change when they do not even show recognition of the correct pronunciation? A lack of recognition or a small effect for correct pronunciations would be more difficult to publish (Ferguson \& Heene, 2012). In order to have publishable results, adjustments to the analysis approach could be made until a significant effect of recognition for correct pronunciations is found. But, these adjustments would also need to be made for the analysis of mispronunciations, which may impact the size of the mispronunciation sensitivity effect. Such a scenario could explain the publication bias suggested by the asymmetry for correct pronunciations in the funnel plot shown in Figure \ref{fig:FunnelCombo} (Simmons, Nelson, \& Simonsohn, 2011). This could lead to an increase in significant results and even alter the measured developmental trajectory of mispronunciation sensitivity measured in experiments.

@@

Considering the variation in findings of developmental change in mispronunciation sensitivity (see Introduction), we next evaluated the developmental trajectory of infants' mispronunciation sensitivity. Our analysis of this relationship revealed a pattern of unchanging sensitivity over infant age and vocabulary size, which has been reported by a handful of studies directly comparing infants over a small range of ages, such as 18-24 months (Bailey \& Plunkett, 2002; Swingley \& Aslin, 2000) or 12-17 months (Zesiger et al., 2012). The lack of age or vocabulary effects in our meta-analysis suggest that this understanding is present from an early age and is maintained throughout early lexical development. We note, however, that despite an increasing publication record of mispronunciation sensitivity studies, fewer than half of the papers included in this meta-analysis measured vocabulary (\emph{n} = 13; out of 32 papers total; see also Figure \ref{fig:Vocabdescribe1}). On the one hand, this may reflect a decreasing interest in the relationship between mispronunciation sensitivity and vocabulary size and/or to invest in data collection that is not expected to yield significant outcomes. On the other hand, non-significant correlations between mispronunciation sensitivity and vocabulary size may be more likely to not be reported, reducing our ability to uncover the true relationship (Rosenthal, 1979; Simonsohn et al., 2014). Considering the theoretical importance of infants' vocabulary size, however, more experimental work investigating and reporting the relationship between mispronunciation sensitivity and vocabulary size, whether the relationship is significant or not, is needed if this link is to be evaluated. We encourage researchers to measure and report infants' vocabulary size in future studies. Nonetheless, if we are to take our results as robust, it becomes thus a pressing open question that theories have to answer which other factors might prompt acquiring and using language-specific phonological contrasts at such an early age.

@@

For several moderators, we found no evidence of significant modulation of mispronunciation sensitivity. Studies that include an unfamiliar, as opposed to familiar distractor image, often argue that the unfamiliar image provides a better referent candidate for mispronunciation than a familiar distractor image, where the name is already known. Yet, no studies have directly examined this assertion and our meta-analysis found that distractor familiarity did not significantly modulate mispronunciation sensitivity. One possible explanation is that when the size of the mispronunciation is small (e.g.~1-feature change), infants are unlikely to map this label onto a novel object and even seem to be biased against doing so (for evidence from infant word learning see Dautriche, Swingley, \& Christophe, 2015; Swingley, 2016; Swingley \& Aslin, 2007).

@@

Variation in measurement standards can have serious consequences, as our analyses show, limiting our ability to draw conclusions. We take this opportunity to make several recommendations to address the issue of varying, potentially post hoc analysis decisions. First, preregistration can serve as proof of a priori decisions regarding data analysis, which can also contain a data-dependent description of how data analysis decisions will be made once data is collected (see Havron, Bergmann, \& Tsuji, 2020 for a primer). The peer-reviewed form of preregistration, Registered Reports, has already been adopted by a large number of developmental journals, and general journals that publish developmental works, showing the field's increasing acceptance of such practices for hypothesis-testing studies. Second, sharing data (Open Data) can allow others to re-analyze existing datasets to both examine the impact of analysis decisions and cumulatively analyze different datasets in the same way. Considering the specific issue of analysis time window, experimenters can opt to analyze the time course as a whole, instead of aggregating the proportion of target looking behavior. This allows for a more detailed assessment of infants' fixations over time and removes the need to reduce the post-naming analysis window. Both Growth Curve Analysis (Mirman, Dixon, \& Magnuson, 2008) and Cluster Permutation Analysis (Maris \& Oostenveld, 2007; Von Holzen \& Mani, 2012) offer potential solutions to analyze the full time course (although Growth Curve Analyses are not without criticism, see Huang \& Snedeker, 2020). Third, it may be useful to establish standard analysis pipelines for mispronunciation studies. This would allow for a more uniform analysis of this phenomenon, as well as aid experimenters in future research planning (see ManyBabiesConsortium, 2020 for a parallel effort). As mentioned previously, one example of standardization would be for all experimenters to measure and report vocabulary size. We hope the above suggestions take us one step closer to this important goal that clarifies the link between internal abilities and behavior in a laboratory study.

@@

\leavevmode\hypertarget{ref-VonHolzen2019}{}%
Von Holzen, K., \& Bergmann, C. (2019). Infant Mispronunciation Sensitivity Meta-Analysis (InMisSens). \url{https://doi.org/10.31234/osf.io/dze29}
